Improving Multi-Domain Neural Machine Translation by Differential Data Selection

### 2021-01-25 2021/acl-ijcnlp2021/mdmt.tex
spelling correction

\begin{document}
\maketitle
\begin{abstract}
  When building machine translation systems, one often needs to make the best out of heterogeneous sets of parallel data in training to achieve the best test performance in one or several domain(s) of interest. This multi-source (multi-domain) adaptation problem is often approached with instance selection or reweighting strategies, most of which pre-supposes an ad-hoc assessment of relevance for training sentences. In this contribution, we study the recently proposed Differential Data Selection (DDS) model  and explore its ability to serve an effective generic framework for these various situations. Our experiments for both domain adaptation and multi-domain learning show that DDS often enables to outperform heuristic training strategy; we also introduce a variant that boosts DDS performance in the presence of adapter modules. 
%   This is a well-known issue, which has given raise to a rich litterature in under the umbrellas of domain adaptation or multi-domain

>>>>

\begin{document}
\maketitle
\begin{abstract}
  When building machine translation systems, one often needs to make the best out of heterogeneous sets of parallel data in training to achieve the best test performance in one or several domain(s) of interest. This multi-source (multi-domain) adaptation problem is often approached with instance selection or reweighting strategies, most of which pre-supposes an ad-hoc assessment of relevance for training sentences. In this contribution, we study the recently proposed Differential Data Selection (DDS) model  and explore its ability to serve an effective generic framework for these various situations. Our experiments for both domain adaptation and multi-domain learning show that DDS often enables to outperform heuristic training strategies; we also introduce a variant that boosts DDS performance of adapter-based multi-domain systems.
%   This is a well-known issue, which has given raise to a rich litterature in under the umbrellas of domain adaptation or multi-domain
